### 2023-08-17 paper/sec-dis-pseudodata.tex
added text and left comments

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 meters from the ATLAS interaction point and has been taking data
since the  beginning of Run III.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume of 830 kg, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

@@

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
 In the following we focus on the AdvSND-far detector.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.
 %
 No information on the expected performance of the AdvSND-far detector
 is available and hence to estimate of the systematic errors
 is carried out.

@@

 With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  while final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
 downstream in the FPF cavern.
 %
 We consider projections both for 10 ton (FLArE-10) and 100 ton (FLArE-100) fiducial volume detectors.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$5\% of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since muon neutrinos would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
 to be the same as those of FASER$\nu$2 as indicated
 in Table~\ref{tab:FPF_experiments}.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
We want to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
When choosing the binning of the measurement, the main criteria are
simplicity and ensuring that Gaussian statistics holds in all bins.

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.85\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
      at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
      energies $\sqrt{s}$ planned as well as to the coverage of existing nuclear neutral- and
      charged-current DIS measurements.
      %
      Bins with less than 30 events have been excluded.
      %
      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
in each bin,
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
$x$ and $Q^2$ associated to each bin.

@@

For each independent source of experimental systematic uncertainty, we hence
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
From Table~\ref{tab:FPF_experiments} we know that its
acceptance parameters and reconstruction performance are specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the absolute difference between the mean number of events in this
bin evaluated for the smeared samples and the
central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
\be
\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
\ee
Individual sources of systematic errors are treated as uncorrelated among them and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.

@@

In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
reaching up to $\sim 40\%$.
%
We recall that measurement of $E_h$ in addition to the leptonic variables is required to
fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
the case of neutral-current scattering.
%
The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
%
For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
for $x\gsim 0.1$, where they are at the few-percent level typically.
%
Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
specially at large-$x$ which is the kinematic region benefitting from the largest event rates.

>>>>

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$ 
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$ {\color{blue} [MF: Is 30 cm correct? The length I have is 100 cm. Looking at \cite{FASER:2023zcr}, I think that the final length of tungsten might be closer to 80cm = 730 layers * 1.1mm/layer]}.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 meters from the ATLAS interaction point and has been taking data
since the  beginning of Run III.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume of 830 kg {\color{blue}[ MF: and length of 35 cm]}, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

@@

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
 In the following we focus on the AdvSND-far detector.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons {\color{blue} [MF: and fiducial length of 50 cm]}.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.
 %
 No information on the expected performance of the AdvSND-far detector
 is available and hence to estimate of the systematic errors
 is carried out.

@@

 With an expected fiducial (active) mass of 10 tons (30 tons) {\color{blue} [MF: and length 3 m]}, FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  while final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
 downstream in the FPF cavern.
 %
 We consider projections both for 10 ton (FLArE-10) and 100 ton (FLArE-100) fiducial volume detectors.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$5\% of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since muon neutrinos would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
 to be the same as those of FASER$\nu$2 as indicated
 in Table~\ref{tab:FPF_experiments}.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
We want to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
When choosing the binning of the measurement, the main criteria are
simplicity and ensuring that Gaussian statistics holds in all bins.{\color{blue} [MF: What does this mean exactly? Binning has not been chosen based on any criteria]}

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields_calculation}) {\color{blue} [MF: There is a discrepancy beyond this. Our integrated cross sections come out a bit smaller. The total cross sections are very sensitive to kinematic cuts. TR and I have talked about this before and I will message] }, when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.85\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
      at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
      energies $\sqrt{s}$ planned as well as to the coverage of existing nuclear neutral- and
      charged-current DIS measurements.
      %
      Bins with less than 30 events have been excluded.{\color{blue}[ MF: Currently, not 30 -  10 for Run3 expt's and 100 for HL-LHC expts]}
      %
      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
in each bin,
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events{\color{blue} [MF: not 30. Currently 10 for Run3, 100 for HL-LHC]}, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
$x$ and $Q^2$ associated to each bin.

@@

For each independent source of experimental systematic uncertainty, we hence
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
From Table~\ref{tab:FPF_experiments} we know that its
acceptance parameters and reconstruction performance are specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By comparing $\mathcal{D}_0$ with the total number of events as calculated by Eq.~(\ref{MCintegration}), we can normalize the distribution to produce the expected yield.{\color{blue} [MF:changed some wording here ]}
%By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
%the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
%to be the absolute difference between the mean number of events in this
%bin evaluated for the smeared samples and the
%central prediction for the number of events
to be the mean of the absolute difference between the number of events in this bin for the smeared samples and the central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
\be
\delta_{\rm sys}^{(E_\ell)} N^{(i)} =\la \Big|  {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
\ee
{\color{blue} [MF:Changed some wording here and the equation slighlty to what we do]}

Individual sources of systematic errors are treated as uncorrelated among them and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.

@@

In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
reaching up to $\sim 40\%$.{\color{blue} [MF: Sometimes uncertainties can be huge more than 100\%. We ignore these bins. Fig 2.4 will also be updated soon probably, and here we will see some larger uncerainties due to the updated cross sections.]}
%
We recall that measurement of $E_h$ in addition to the leptonic variables is required to
fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
the case of neutral-current scattering.
%
The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
%
For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
for $x\gsim 0.1$, where they are at the few-percent level typically.
%
Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
specially at large-$x$ which is the kinematic region benefitting from the largest event rates.
